Leadership across cultures and contexts: an exploratory analysis

### 2020-06-18 leadership_across_cultures_contexts.Rmd

Our fourth goal was to explore lower dimensional representations of these data that might reveal informative "features." These included logistic PCA, minimal spanning trees and nearest neighbors (mst-kNN), and hierarchical cluster analysis. See the SI for descriptions of these methods. Our fifth goal was to assess variation in our lower-dimensional "features" by group context, subsistence strategy, continental region, and leader sex, using logistic mixed effects models fit with the lme4 package. Our sixth goal was to evaluate the features in light of influential evolutionary theories of leadership. Drawing on the empirically derived features as a guide, we aimed to construct "elements" of leadership that corresponded to elements of influential theories, examining intersections of these elements across all text records.

>>>>

Our fourth goal was to explore lower dimensional representations of these data that might reveal informative "features." These included logistic PCA, minimal spanning trees and k-nearest neighbors (mst-kNN), and hierarchical cluster analysis. See the SI for descriptions of these methods. Our fifth goal was to assess variation in our lower-dimensional "features" by group context, subsistence strategy, continental region, and leader sex, using logistic mixed effects models fit with the lme4 package. Our sixth goal was to evaluate the features in light of influential evolutionary theories of leadership. Drawing on the empirically derived features as a guide, we aimed to construct "elements" of leadership that corresponded to elements of influential theories, examining intersections of these elements across all text records.
